\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue, roman]{casual}
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classic}                % idem

\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{url}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Jiashun}
\familyname{Zhu}
\title{Curriculum Vitae}
\mobile{+86 13764325590}
\email{zhujiashun2010@gmail.com}
%% \quote{``Do what you fear, and the death of fear is certain.''\\-- Anthony Robbins}

%\phone{(312) 413-8265}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
%\photo[64pt]{avatar.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file;

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%% \renewcommand*{\sectionfont}{\LARGE\sffamily\monospace\slshape}
%% \renewcommand*\addressfont{\fontfamily{pzc}\selectfont}
%% \renewcommand*\sectionfont{\fontfamily{pzc}\fontsize{20}{24}\selectfont}

\begin{document}
\maketitle

\section{Education}
%%\cventry{2010--Present}{Undergraduate}{Shanghai JiaoTong University}{expected 2014}{}
\cventry{2010--2014}{Undergraduate}{Shanghai JiaoTong University}{}{}
{
\begin{itemize}
\item \textbf{Major}: Computer Science and Engineering
\item \textbf{Rank}: 21/122
%\item \textbf{MajorCourse/Score}: Algorithm and Complexity(96), Discrete Mathematics(98), Operating System(93), Compiler(90), Computer architecture(91), Computer Organization Experiment(92), C++ programming(91), Linear Algebra(94), Artificial Intelligence(93), Computer Network(92), Database(90) and so on.\\
\end{itemize}
}
\cventry{2014--present}{Graduate}{Shanghai JiaoTong University}{}{}
{
\begin{itemize}
\item \textbf{Major}: Computer Science and Engineering
\end{itemize}
}

%\section{Master thesis}

%\section{Master thesis}
%\cvline{title}{\emph{Title}}
%\cvline{supervisors}{Supervisors}
%\cvline{description}{\small Short thesis abstract}


\section{Community}
%\cventry{TechBlog}{\href{http://blog.csdn.net/Zyearn}}{}{}{}{}
%\cventry{MindBlog}{\url{http://zyearn.github.io}}{}{}{}{}
\cventry{Blog}{\url{http://www.lifeofzjs.com}}{}{}{}{}
%\cventry{OldBlog}{http://blog.csdn.net/Zyearn}{}{}{}{}
\cventry{Github}{\url{https://github.com/zyearn}}{}{}{}{}

%\section{Academic Experience}
%\cventry{2013.9--now}{Research Assistant}{Reliable adaptive distributed systems laboratory}{}{}
%{
%\begin{itemize}
%\item Advisor: \href{http://www.cs.sjtu.edu.cn/~fwu/index.html}{Fan Wu(http://www.cs.sjtu.edu.cn/~fwu/index.html)}
%    \item \textbf{interest}: Memory computing, Operating system.
%\end{itemize}
%}


\section{Internship Experience}
%SSG STO Big Data Technology
%Intel Asia-Pacific Research & Development Ltd.

\cventry{2016.6--now}{Shanghai Qiniu Technology Co., Ltd}{}{}{}
{
\begin{itemize}
\item position: server-side engineer\\
I participate in the design and implementation of the system in core product line(Fusion CDN).
\end{itemize}
}

\cventry{2015.6--2015.9}{Tencent Technology (Shenzhen) Co., Ltd}{}{}{}
{
\begin{itemize}
\item position: Interactive Entertainment Group/Aurora Studios/game server-side intern engineer\\
    I completed a game server system designed for intern engineers, which involves user login, simple user interactions, user logout and user data persistency. 
\end{itemize}
}

\cventry{2014.6--2014.12}{INESA Holding Group R\&D Center}{}{}{}
{
\begin{itemize}
\item Position: Front-end/Back-end intern software engineer\\
I was involved in the development of back-end server using NodeJS and front-end parts using JavaScript/HTML/CSS.
\end{itemize}
}

\cventry{2013.8--2014.2}{Shanghai YiTu Network Technology Co., Ltd}{}{}{}
{
\begin{itemize}
\item Position: Linux C++ intern software engineer\\
I was involved in the architecture design and implementation of back-end services. I learned many other valuable things other than technical skills, e.g., how to cooperate with others, what is important in work and so on.
\end{itemize}
}

\section{Project Experience}
%% \subsection{Research Projects}
\cventry{2015--now}
{Zaver}
{yet another fast and efficient HTTP server}
{open source project}
{}
{
\begin{itemize}
    \item project link: \url{https://github.com/zyearn/zaver}
\end{itemize}
The purpose of Zaver is to help developers understand how to write a high performance server based on epoll. Although Nginx is a good learning example, its complexity and huge code base make people discouraged. Zaver uses as few codes as possible to demonstrate the core structure of high performance server like Nginx. Developers can lay a solid foundation by learning Zaver for further study in network programming.
}
\vspace*{0.2\baselineskip}

\cventry{2015.12--2016.3}
{JOS}
{an OS kernel}
{course project}
{}
{
\begin{itemize}
    \item project link: \url{https://github.com/zyearn/6.828-labs}
\end{itemize}
This is the lab project of MIT6.828, in which students will write a small Exokernel. In this project, I implemented a kernel supporting memory management, process, exception/interrupt, syscall, page fault, multi-core support, scheduler, COWfork, preemptive kernel, IPC, file system, network and other basic features.
}
\vspace*{0.2\baselineskip}

\cventry{2015.6-2015.9}
{A small game server system}
{tencent intern project}
{}
{}
{
This project is designed for intern engineers to get start in game server programming. I implemented a system supporting user login, simple user interactions, user logout and user data persistency. The difficult part is how to design a reliable and fault-tolerant back-end system.
}
\vspace*{0.2\baselineskip}

\cventry{2014.10-2014.12}
{CE Online}
{HTML, JavaScript, NodeJs, Express, Mysql}
{outsourcing Project}
{}
{
\begin{itemize}
    \item project link: \url{http://ece114.com}
\end{itemize}
This project aimed at writing a portal website of electron component for a startup team. In the back end, we use NodeJS framework, Express, which is suitable for I/O intensive task. We use Mysql as our database. My job involves part of front-end development and back-end development.
}
\vspace*{0.2\baselineskip}

\cventry{2012.10-2012.12}
{A Compiler for SmallC}
{C, Flex, Yacc, Recursive-Descent Parser}
{Course Project}
{}
{
\begin{itemize}
    \item project link: \url{https://github.com/zyearn/SmallC}
\end{itemize}
This project involves the whole process how advanced language are compiled into assembly language.
I use Flex to do lexical analysis, Yacc to do syntax analysis and generate target code(x86) using recursive-descent method.
}

%\vspace*{0.2\baselineskip}
%\cventry{2013.12--2014.2}
%{Design API and implement SDK of services provided by intern company}
%{C++}
%{company Projoct}
%{}
%{
%Customers need an interface to access services provided by company. My task is to design API and to implement it robustly in C++.\\
%}


%\cventry{2012.4--2012.6}
%{Implementing a File System for Operating System}
%{C}
%{Course Project}
%{Score:93/100}
%{
%Using C writing a FileSystem. Big file in the real disk are used to simulate the virtual disk. Design Priciple is Inode, which is excellent data structure for file system.\\
%Here is the ppt demo when I did my presentation: \url{http://zjsblog.com/others/OSreport.pdf}\\
%}

\section{Awards}
\cventry{2015}{Shanghai JiaoTong University scholarship}{}{}{}{}
\cventry{2014}{Shanghai JiaoTong University scholarship}{}{}{}{}
\cventry{2013}{Shanghai JiaoTong University scholarship}{}{}{}{}
\cventry{2013}{First prize in CCF Hackathon at Shanghai JiaoTong University}{}{}{}{}
\cventry{2011}{Shanghai JiaoTong University scholarship}{}{}{}{}

\section{Standardized Test}
\cventry{CET 6}{559}{}{}{}{}


\section{Skills}
\cventry{Language/Platform}{C, C++, Go, NodeJS/JavaScript, SQL, Python, Shell}{}{}{}{}
\cventry{Document}{LaTex, Vim}{}{}{}{}
\cventry{Tools}{Git, MacOSX/Linux}{}{}{}{}
%\cventry{Games}{Warcraft 3}{}{}{}{}

% \closesection{}                   % needed to renewcommands
% \renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

\end{document}
